### 2023-06-23 bachelorthesis/21-motion.tex
#37, #39: Redo circular motion picture and some grammar

\begin{center}
    \captionsetup{type=figure}
    \begin{tabular}{c c c c c c}
        \input{../pictures/Theory/Lorentz-Force_Thesis.tex} &
        \input{../pictures/Theory/Electric-Force.tex} &
        \input{../pictures/Theory/Inhomogenous-Magnetic-Field.tex}\\[0.3cm]
        \textbf{(a)} & \textbf{(b)} & \textbf{(c)} \\
    \end{tabular}
    \captionof{figure}{Forces acting on a charged particle:\\
        \begin{tabular}{l l}
            \textbf{(a)} & Lorentz force $\vect{F}_{\perp, B}$ perpendicular to velocity $\vect{v}$ which causes,\\
                         & circular motion with Lamor radius $\rho_\mathrm{L}$ and cyclotron frequency $\omega_\mathrm{c}$ \\
            \textbf{(b)} & Electric force $\vect{F}_{\parallel,E}^\pm$,\\
            \textbf{(c)} & Mirror effect with force $\vect{F}_{\parallel,\nabla_{\!\parallel} B}$ and magnetic moment $\mu$ \\
                         & caused by an inhomogeneous magnetic field $\vect{B}$.  \\
        \end{tabular}
    }
    \label{fig:perp-par-motion}
\end{center}

>>>>

\begin{center}
    \captionsetup{type=figure}
    \begin{tabular}{c c c c c c}
        \input{../pictures/Theory/Lorentz-Force_Thesis.tex} &
        \input{../pictures/Theory/Electric-Force.tex} &
        \input{../pictures/Theory/Inhomogenous-Magnetic-Field.tex}\\[0.3cm]
        \textbf{(a)} & \textbf{(b)} & \textbf{(c)} \\
    \end{tabular}
    \captionof{figure}{Forces acting on a charged particle:\\
        \begin{tabular}{l l}
            \textbf{(a)} & Lorentz force $\vect{F}_{\perp, B}$ perpendicular to velocity $\vect{v}^\pm$ and \\
                         & magnetic field $\vect{B}$ which causes, circular motion with different directions for \\
                         & electron and ions, Lamor radius $\rho_\mathrm{L}$ and cyclotron frequency $\omega_\mathrm{c}$, \\
            \textbf{(b)} & Electric force $\vect{F}_{\parallel,E}^\pm$ with electric field $\vect{E}$,\\
            \textbf{(c)} & Mirror effect with force $\vect{F}_{\parallel,\nabla_{\!\parallel} B}$ and magnetic moment $\mu$ \\
                         & caused by an inhomogeneous magnetic field $\vect{B}$.  \\
        \end{tabular}
    }
    \label{fig:perp-par-motion}
\end{center}

### 2023-06-23 briefcommunication/briefcommunication.tex
#37: Fixed spacing
#37, #39: Redo circular motion picture and some grammar

\title[Size convergence of the $\exb$ staircase pattern in flux tube simulations of ion temperature gradient driven turbulence]
{Size convergence of the $\exb$ staircase pattern in flux tube simulations of ion temperature gradient driven turbulence}

@@

%% Include graphic for two column with specific place
\onecolumngrid
\begin{center}
	\centering
	\captionsetup{type=figure}
	\includegraphics[width=0.85\textwidth]{Briefcommunication/1.pdf}
	\captionof{figure}{
		\textbf{(a)} Time traces of the heat conduction coefficient $\chi$ for $\rlt = 6.0$ for radial increased box sizes,\\
		\textbf{(b)} Time traces of $\hatwexbamp$ for radial increased box sizes.
	}
	\label{fig:wexb-eflux-1-2-3-4x1-comparison}
\end{center}
\twocolumngrid

@@

In the final test the inverse background temperature gradient length $\rlt$ is varied at fixed $3\times3$ box size.
Since suppression of turbulence usually occurs at later times when approaching the finite heat flux threshold from below \cite{Peeters2016}, the analysis aims to lengthen the phase during which the zonal flow varies in time due to turbulent Reynolds stresses.
This scan covers realizations with $\rlt \in [6.0,~6.2,~6.4]$.
In the case of $\rlt = 6.2$ turbulence suppression is observed for $t > 11000\,R/\vth$, while stationary turbulence during the entire simulation time trace of $12000\,R/\vth$ is found for $\rlt = 6.4$.
The finite heat flux threshold, hence, is $\rlt|_\mathrm{finite} = 6.3 \pm 0.1$ in accordance with Ref. \onlinecite{Peeters2016}.
Although the initial quasi-stationary turbulence in the former case is significantly longer compared to the $\rlt = 6.2$ realization discussed in the second test, a stationary pattern with basic zonal flow mode $\nzf = 3$ establishes. 
Again, the $\nzf = 1$ (box scale) zonal flow mode does not grow secularly during the entire turbulent phase.
Also, this test confirms the statistical soundness of the converged pattern size of $\sim 57 - 76\,\rhoth$. \bigskip

>>>>

\title[Size convergence of the $\exb$ staircase pattern in flux tube simulations of ion temperature gradient-driven turbulence]
{Size convergence of the $\exb$ staircase pattern in flux tube simulations of ion temperature gradient-driven turbulence}

@@

%% Include graphic for two column with specific place
\onecolumngrid
\begin{center}
	\centering
	\captionsetup{type=figure}
	\includegraphics[width=0.\textwidth]{Briefcommunication/1.pdf}
	\captionof{figure}{
		\textbf{(a)} Time traces of the heat conduction coefficient $\chi$ for $\rlt = 6.0$ for radial increased box sizes,\\
		\textbf{(b)} Time traces of $\hatwexbamp$ for radial increased box sizes.
	}
	\label{fig:wexb-eflux-1-2-3-4x1-comparison}
\end{center}
\twocolumngrid

@@

In the final test the inverse background temperature gradient length $\rlt$ is varied at fixed $3\times3$ box size.
Since suppression of turbulence usually occurs at later times when approaching the finite heat flux threshold from below \cite{Peeters2016}, the analysis aims to lengthen the phase during which the zonal flow varies in time due to turbulent Reynolds stresses.
This scan covers realizations with $\rlt \in [6.0,~6.2,~6.4]$.
In the case of $\rlt = 6.2$ turbulence suppression is observed for $t > 11000\,R/\vth$, while stationary turbulence during the entire simulation time trace of $12000\,R/\vth$ is found for $\rlt = 6.4$.
The finite heat flux threshold, hence, is $\rlt|_\mathrm{finite} = 6.3 \pm 0.1$ in accordance with Ref. \onlinecite{Peeters2016}.
Although the initial quasi-stationary turbulence in the former case is significantly longer compared to the $\rlt = 6.2$ realization discussed in the second test, a stationary pattern with basic zonal flow mode $\nzf = 3$ establishes. 
Again, the $\nzf = 1$ (box scale) zonal flow mode does not grow secularly during the entire turbulent phase.
Also, this test confirms the statistical soundness of the converged pattern size of $\sim 57 - 76\,\rhoth$.\\

\bigskip

### 2023-06-23 pictures/Theory/Lorentz-Force.tex
#37, #39: Redo circular motion picture and some grammar

\begin{tikzpicture}
    % Circle
    \draw (0,0) circle (1.5);
    \filldraw (0,0) circle (1.5pt);
    % Force
    \draw[thick, Notagrey, <-] (90:0.5) node[right, Notagrey]{$\vect{F}_{\perp, B}$} -- ++ (90:1.0) node[coordinate] (x) {};
    % Larmor radius
    \draw[thick, black, ->] (0,0) -- ++(0:1.5);
    \draw (0.6,-0.4) node {$\rho_\mathrm{L} = \frac{mv_{\perp}}{|q|B}$};
    % Velocity
    \draw[thick,Notaorange, ->] (x) -- ++(180:1cm) node[above, Notaorange]{$\vect{v}$};
    % Cyclontron freqency
    \draw[thick, ->, Notared] (200:1.1*1.5) arc(200:240:1.1*1.5);
    \draw (240:1.4*1.5) node[Notared] {$\omega_\mathrm{c} = \frac{|q|B}{m}$};
    % Particle
    \filldraw [Notablue] (x) circle (2pt);
    \draw (x) node[above right, Notablue]{Particle};
    % Magnetic field
    \draw [thick, Notagreen] (1.5,-1.5) circle (0.2);
    \filldraw [Notagreen] (1.5,-1.5) circle (1.5pt);
    \draw (1.8,-1.2) node[Notagreen]{$\vect{B}$};
\end{tikzpicture}

>>>>

\begin{tikzpicture}
    % Circle
    \draw[lightgray] (0,0) circle (1.5);
    \filldraw (0,0) circle (1.5pt);
    % Force
    \draw[thick, Notagrey, <-] (90:0.5) node[right, Notagrey]{$\vect{F}_{\perp, B}$} -- ++ (90:1.0) node[coordinate] (x) {};
    % Larmor radius
    \draw[thick, black, ->] (0,0) -- ++(0:1.5);
    \draw (0.6,-0.4) node {$\rho_\mathrm{L} = \frac{mv_{\perp}}{|q|B}$};
    % Velocity
    \draw[thick,Notaorange, ->] (x) -- ++(180:1cm) node[left, Notaorange]{$\vect{v}^-$};
    \draw[thick,Notaorange, ->] (0,-1.5) -- ++(180:1cm) node[left, Notaorange]{$\vect{v}^+$};
    % Cyclontron freqency
    \draw[thick, ->, blue] (90:1.0*1.5) arc(90:150:1.0*1.5);
    \draw[thick, <-, red] (210:1.0*1.5) arc(210:270:1.0*1.5);
    \draw (50:1.5*1.5) node[black] {$\omega_\mathrm{c} = \frac{|q|B}{m}$};
    % Charges
    \draw [fill=blue, blue] (x) circle (0.2) node[white, font=\boldmath]{$-$};
    \draw [fill=red, red] (0,-1.5) circle (0.2) node[white, font=\boldmath]{$+$};
    % Magnetic field
    \draw [thick, Notagreen] (1.5,-1.5) circle (0.2);
    \filldraw [Notagreen] (1.5,-1.5) circle (1.5pt);
    \draw (1.8,-1.2) node[Notagreen]{$\vect{B}$};
\end{tikzpicture}
